Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`

### 2024-08-29 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
Try to debug k.weight

---
title: "Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

@@

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)
s <- Azimuth::RunAzimuth(srat, reference ="fetusref")

>>>>

---
title: "Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
  is_ci: FALSE
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

Determine whether or not this notebook is being run in GitHub Actions.

```{r setup_ci}
# Adapted from: https://github.com/AlexsLemonade/OpenPBTA-analysis/blob/e854738b57b16c3725673ad63b4ffd20ec48ad19/analyses/gene-set-enrichment-analysis/02-model-gsea.Rmd#L44-L52
# Assigning params$is_ci to running_in_ci avoids a locked binding error
running_in_ci <- params$is_ci

# Are we testing? In case of a non 0/1 number, we recast as logical, and then ensure logical.
if (running_in_ci %in% c(0,1)) running_in_ci <- as.logical(running_in_ci)
if (!(is.logical(running_in_ci))) {
  stop("\n\nERROR: The parameter `is_ci` should be FALSE/TRUE (or 0/1).")
}
```

@@

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)

# If running in CI, there will be fewer cells and we must set k.weight in
# RunAzimuth() to a lower value
if (running_in_ci) {
  k_weight <- 2
} else {
  k_weight <- 50  # The default value
}

print(k_weight)
s <- Azimuth::RunAzimuth(srat, reference ="fetusref", k.weight = k_weight)

### 2024-08-29 analyses/cell-type-wilms-tumor-06/notebook_template/02b_label-transfer_fetal_kidney_reference_Stewart.Rmd
Try to debug k.weight

---
title: "Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

### Load the pre-processed `Seurat` object
```{r load, message=FALSE, warning=FALSE}
# open the processed rds object
srat <- readRDS(file.path(data_dir, paste0("00a-fetal_full_label-transfer_",params$sample_id,".Rds")))
```

@@

data <-  RunAzimuth(srat, path_to_reference, assay = 'RNA')
# We transfer the annotation to the pre-processed `Seurat`object as we don't want to keep changes done on the query by `RunAzimuth`
metadata_vec <- c("predicted.compartment.score", "predicted.compartment", "predicted.cell_type.score", "predicted.cell_type")
metadata_to_trasfer <- s@meta.data[, metadata_vec]
srat <- AddMetaData(srat, metadata_to_trasfer, col.name = paste0("fetal_full_", metadata_vec))
```

@@

```{r save}
saveRDS(object = srat, file = file.path(output_dir, paste0("00b-fetal_kidney_label-transfer_",params$sample_id,".Rds")))
```

>>>>

---
title: "Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
  is_ci: FALSE
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

### Load the pre-processed `Seurat` object
```{r load, message=FALSE, warning=FALSE}
# open the processed rds object
srat <- readRDS(file.path(data_dir, paste0("02a-fetal_full_label-transfer_",params$sample_id,".Rds")))
```

@@

# If running in CI, there will be fewer cells and we must set k.weight in
# RunAzimuth() to a lower value
if (running_in_ci) {
  k_weight <- 10
} else {
  k_weight <- 50  # The default value
}

data <-  RunAzimuth(srat, path_to_reference, assay = 'RNA', k.weight = k_weight)
# We transfer the annotation to the pre-processed `Seurat`object as we don't want to keep changes done on the query by `RunAzimuth`
metadata_vec <- c("predicted.compartment.score", "predicted.compartment", "predicted.cell_type.score", "predicted.cell_type")
metadata_to_trasfer <- data@meta.data[, metadata_vec]
srat <- AddMetaData(srat, metadata_to_trasfer, col.name = paste0("fetal_kidney_", metadata_vec))
```

@@

```{r save}
saveRDS(object = srat, file = file.path(output_dir, paste0("02b-fetal_kidney_label-transfer_",params$sample_id,".Rds")))
```
